Recursive Neural Network Part-of-Speech Tagger

### 2013-12-21 paper/paper.tex
Revise abstract.

\begin{document}
\maketitle
\begin{abstract}
We use a recursive neural network (RNN) on part-of-speech tagging task (POS). There are two models are proposed and implemented, basic RNN and Compositional Vector Tagger(CVT) RNN. The performance of basic RNN is close to the HMM model and with high probability beat it if captialization information is captured. The forever tagging time of CVT model we do not analysis. We tried some very useful neural network training trics and detailly analysis the performance of basic RNN, such as verifying the contribution of sequential information and error rates of different parts of sentence and so on.
\end{abstract}

>>>>

\begin{document}
\maketitle
\begin{abstract}
We use a recursive neural network (RNN) on a part-of-speech tagging task (POS). We propose and implement two models: a basic RNN and a Compositional Vector Tagger (CVT) RNN. The performance of the basic RNN is close to the HMM model and with high probability will beat it if capitalization information is captured. The intractable tagging time of the CVT model means we cannot analyze it. We tried some useful neural network training tricks and carefully analyze the performance of the basic RNN model, such as verifying the contribution of sequential information and error rates of different parts of sentences.
\end{abstract}
